---
title: "Legal Comprehension & Summarizing via Annotation I Project"
author: "Jessica Macaluso"
date: "2025-03-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, let's disable scientific notation and then read in `tidyverse`.

```{r sci_notation}
options(scipen = 999) 
```

```{r packages}
library(tidyverse)
```

Next, let's read in our dataframes.

Here is our Cohen's Kappa annotation data.

```{r data1}
kappa <- read.csv(file='kappa2_F22_F23.csv')
head(kappa)
```

Here is our writing test performance dataframe.

```{r data2}
writing <- read.csv(file='writing2_F22_F23.csv')
head(writing)
```

Now, let's merge our dataframes by participant.

```{r merge}
merge(kappa, writing, by='ID', all = TRUE) -> full_F22_F23
head(full_F22_F23)
```

```{r nrow}
nrow(full_F22_F23)
```

We have 35 participants/students from both Fall 2022 and Fall 2023.

Let's make a new dataframe with just the columns of interest.

```{r data3}
simple_df <- full_F22_F23 %>% select(ID, Group.x, Test1, Test2,
                                     kappa_avg, WritingTest1, WritingTest2)
simple_df <- rename(simple_df,c("Group" = "Group.x"))
simple_df <- rename(simple_df,c("KappaAverage" = "kappa_avg"))
simple_df
```

Let's visualize our data!

```{r plot1}
ggplot(data = simple_df, aes(x = KappaAverage, y = WritingTest1, color = Group)) + 
  geom_point(size = 8) +
  geom_smooth(method = "lm", se = FALSE, fullrange = TRUE, aes(color = Group), size = 5) +
  labs(x = "Cohen's Kappa Annotation Accuracy",
       y = "Writing Test 1 Performance",
       title = "Positive Relationship: as Writing Test 1 Performance Increases, Annotation Accuracy Increases for Both Gloss Groups") +
  theme_classic()
```

```{r plot2}
ggplot(data = simple_df, aes(x = KappaAverage, y = WritingTest2, color = Group)) + 
  geom_point(size = 8) +
  geom_smooth(method = "lm", se = FALSE, fullrange = TRUE, aes(color = Group), size = 5) +
  labs(x = "Cohen's Kappa Annotation Accuracy",
       y = "Writing Test 2 Performance",
       title = "Gloss Helps Weaker Students Catch Up: Softens Relationship Between Early Accuracy & Writing Test 2 Performance") +
  theme_classic()
```

Let's run a few regression models to understand our findings. 

```{r regression1}
model3 <- lm(WritingTest1 ~ 1 + KappaAverage + Group, data = simple_df)
model3 %>% summary()
```

No significant effects.

```{r regression4}
model4 <- lm(WritingTest2 ~ 1 + KappaAverage + Group, data = simple_df)
model4 %>% summary()
```

Yes, significant differences for Cohen's Kappa when looking at WritingTest2 performance.
